---
title: "April 2018 Bug BBQ"
date: April 12-13, 2018
output: html_document
---

```{r setup, echo=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


```{r, echo=FALSE, message=FALSE}
library(tidyverse)
library(glue)

repos <- tibble::tribble(
  ~repo_nm, ~org, ~primary, ~Lesson, ~slack_id, ~slack_slug, 
  ## social sciences -----------------------------------------------------------
  "spreadsheets-socialsci", "dc", TRUE, "Spreadsheets for Social Sciences", "C9X34DJ9Z", "dc-socsci-data-org", 
  "openrefine-socialsci", "dc", TRUE, "OpenRefine for Social Sciences", "C9Y0UEXPY", "dc-socsci-openref", 
  "r-socialsci", "dc", TRUE, "R for Social Sciences", "C9X9JDTSR", "dc-socsci-r", 
  "python-socialsci", "dc", TRUE, "Python for Social Sciences", "C9WJEBW01", "dc-socsci-py-sosci", 
  "sql-socialsci", "dc", TRUE, "SQL for Social Sciences", "C9Y6QJZ8F", "dc-socsci-sql",
  ## Geospatial ----------------------------------------------------------------
  "R-spatial-raster-vector-lesson", "dc", TRUE, "Intro to Geospatial Data With R", "C9ME7G5RD", "dc-geospatial",  
  "r-spatial-data-management-intro", "dc", TRUE, "Intro to Geospatial Data", "C9ME7G5RD", "dc-geospatial", 
  ## Ecology  ------------------------------------------------------------------
  "R-ecology-lesson", "dc", FALSE, "Manipulation and Visualization of Ecological Data with R", "C9X9EC405", "dc-ecology-r", 
  "python-ecology-lesson", "dc", FALSE, "Python for Ecologists", "C9X44HCDS", "dc-ecology-py", 
  ## Spanish Lesson ------------------------------------------------------------
  "r-novice-gapminder-es", "swc", FALSE, "R para Análisis Científicos Reproducibles", "C9X9DN84V", "swc-r-gapminder-es", 
  ## Instructor training -------------------------------------------------------
  "instructor-training", "cc", FALSE, "Instructor Training", "C0CP2ERHA", "instructor-training", 
  ) %>%
  mutate(
    org_ = case_when(org == "dc" ~ "datacarpentry",
                     org == "swc" ~ "swcarpentry",
                     org == "lc" ~ "librarycarpentry",
                     org == "cc" ~ "carpentries", 
                     TRUE ~ ""
    ),
    slack_slug = gsub("-", "--", slack_slug), 
    Site = glue::glue("[Website](https://{org_}.github.io/{repo_nm}/)"),
    `All Issues` = glue::glue("[GitHub](https://github.com/{org_}/{repo_nm}/issues)"), 
    Slack = glue::glue("[![Slack Channel](https://img.shields.io/badge/Slack_Channel-{slack_slug}-E01563.svg)](https://swcarpentry.slack.com/messages/{slack_id}/)")
  )



primary_table <- repos %>%
  filter(primary) %>%
  select(Lesson, `All Issues`, Site, Slack)

secondary_table <- repos %>%
  filter(!primary) %>%
  select(Lesson, `All Issues`, Site, Slack)

```


## Communication

We'll get organized with Slack. If you don't already have an account, you can [create one](https://swc-slack-invite.herokuapp.com/).

Most lessons have their own Slack channel. They are accessible from the README file in their respective GitHub repositories. To coordinate across lessons, we also set up channels for the Social Sciences and Geospatial curricula:

* [Social Science Slack channel](https://swcarpentry.slack.com/messages/C9M87MC7Q)
* [Geospatial Slack channel](https://swcarpentry.slack.com/messages/C9ME7G5RD)

If you have any questions, you are always welcome to ask them on the [General Slack channel](https://swcarpentry.slack.com/messages/C03LE48AY).

### How to get involved and contribute?

Review our [Bug BBQ guide](https://hackmd.io/s/r1EDctqcG#).

Look for issues with the <span style="font-family: monospace; font-weight: bold; color: #222222; background-color: #FFEB3A; border-radius: 4px; padding: 4px;">good first issue</span> or the <span style="font-family: monospace; font-weight: bold; color: #222222; background-color: #FFF8C4; border-radius: 4px; padding: 4px;">help wanted</span> labels among the issues in the lesson repositories.

### Main lessons

```{r}
knitr::kable(primary_table, format = "html") %>%
  kable_styling(bootstrap_options = "striped", full_width = TRUE) %>% 
  kableExtra::column_spec(1, width = "60%")

```

### Other lessons

```{r}
knitr::kable(secondary_table, format = "html") %>%
  kable_styling(bootstrap_options = "striped", full_width = TRUE) %>% 
  kableExtra::column_spec(1, width = "60%")
```

## Local Sites

If you'd like to add your local group to the list of participating institutions to the Bug BBQ, please [open an issue](https://github.com/carpentries/2018-04-bug-bbq/issues/new?template=local-event.md).

```{r}
local_sites <- tibble::tribble(
  ~Organization, ~Address, ~lat, ~long, ~date_time, ~contact_person,
  "University of Florida", "Informatics Institute Lecture Room", 29.6480513, -82.3444175, "Friday April 13th (1pm - 5pm)", "[Hao Ye](https://github.com/UF-Carpentry/Coordination/issues/11)"
)

library(leaflet)

map <- leaflet() %>%
  addProviderTiles(providers$CartoDB.Positron) %>% 
  addMarkers(lng = local_sites$long,
    lat = local_sites$lat,
    popup = glue::glue("<b>{org}</b> <br> {address} <br> {date_time}",
      org = local_sites$Organization,
      address = local_sites$Address, 
      date_time = local_sites$date_time))
```


```{r}
local_sites %>%
    select(Organization, "Date/Time" = date_time,
           "Contact Person" = contact_person) %>% 
    knitr::kable()
```

```{r}
map
```


